---
title: "Regional Resources"
---

<center>
<i class="fas fa-hard-hat fa-3x" aria-hidden="true"></i> Under Construction! <i class="fas fa-hard-hat fa-3x" aria-hidden="true"></i>
</center>

- **Keywords**: aid, Black, funding, gender identity, health, housing, LGBTQ,
sex work

```{r, include=FALSE}
library(tidyverse)
library(DT)
```

```{r, echo=FALSE, message=FALSE}
## Load resource list
## Note: If you encounter issues with characters, try resaving the
## CSV as a UTF-8 CSV. Excel... does not like interpreting as UTF-8
data <- read_csv("regional_resources.csv", comment = "#")

## Make website a hyperlink
#data$Website <- paste0("<a href='",data$Website,"' target='_blank'>",data$Website,"</a>")
#data <- select(data, -c(ShortLink))

## Make website a hyperlink
data$Website <- paste0("<a href='",data$Website,"' target='_blank'>",data$Website,"</a>")

## Need to keep 1st column when doing buttons so the CSV renders properly
datatable(data,
    rownames=FALSE,
    escape = FALSE,
    extensions = c('Responsive', 'Buttons', 'SearchBuilder'), 
    options = list(
    dom = 'QBfrtip',
##    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')),
    buttons = list(
      'copy', 'csv', 'excel',
      list(extend = 'pdf', 
           orientation = 'landscape',
           exportoptions=list(pageSize='A3',
           customize = JS("function(doc){doc.styles.tableHeader.color='purple';}")
                )),
      'print')
))
```

Do you have a resource that you'd like to see added? Fill out our
<a href="https://forms.gle/VpkzjtbuAes3beAr7">suggestion form</a>.

## Disclaimer
This website offers resources and information, and is designed for educational
purposes only.
The T.H.R.I.V.E. website may contain links to external websites that are not
provided or maintained by or in any way affiliated with T.H.R.I.V.E.
Please note we don't guarantee the accuracy, relevance, timeliness, or
completeness of any information on these websites.
You should not rely on this information as a substitute for, nor does it
replace, professional medical advice, diagnosis or treatment.
