---
title: "Crisis Resources"
---

- **Keywords**: AAPI, abuse, academia, aid, app, Black, career, coping, COVID-19, 
detransition, disability, disaster, disordered eating, education, end-of-life, 
food, funding, gender identity, general, gestation, grief, harm reduction, 
health, HIV, housing, hotline, Indigenous, Latinx, legal, LGBTQ, mental health,
mentoring, MPX, neurodivergence, non-carceral, online safety, parent, pet, psychosis, providers, 
protest, relationships, religion, STEMM, substance use, support, under 18,
veteran
- **Region/Languages**: UK, Canada, international, Espa&ntilde;ol

<center>
[Click here for a list of non-carceral support options](https://drive.google.com/file/d/1C3RJpE2o2W5cKM78pdCigVXQEMGMC1hz/view?usp=drive_link)
</center>

```{r, include=FALSE}
library(tidyverse)
library(DT)

print("HI!")
```

```{r, echo=FALSE, message=FALSE}
## Load resource list
## Note: If you encounter issues with characters, try resaving the
## CSV as a UTF-8 CSV. Excel... does not like interpreting as UTF-8
## Find the bad UTF-8 lines
# library("xfun")
# read_utf8("thrive_resources.csv")
data <- read_csv("thrive_resources.csv", comment = "#")

## Make website a hyperlink
data$Website <- paste0("<a href='",data$Website,"' target='_blank'>",data$Website,"</a>")
data <- select(data, -c(ShortLink))


### Make URLs a hyperlink
#data$ShortLink <- paste0("<a href='https://",data$ShortLink,"' target='_blank'>","https://",data$ShortLink,"</a>")

### Remove ShortLink column, because they're broken
#data <- select(data, -c(ShortLink))

### Remove website column, since it's just an explanation for the ShortLink
#data <- select(data, -c(Website))

## Remove first resource column, since website includes the same name
#data <- select(data, -c(Resource))

## Change to factor-based data for "tagged" search
# data$Category <-as.factor(data$Category)
# data$Type <-as.factor(data$Type)

## Need to keep 1st column when doing buttons so the CSV renders properly
datatable(data,
    rownames=FALSE,
    escape = FALSE,
    extensions = c('Responsive', 'Buttons', 'SearchBuilder'), 
    options = list(
    dom = 'QBfrtip',
##    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')),
    buttons = list(
      'copy', 'csv', 'excel',
      list(extend = 'pdf', 
           orientation = 'landscape',
           exportoptions=list(pageSize='A3',
           customize = JS("function(doc){doc.styles.tableHeader.color='purple';}")
                )),
      'print')
))

## Need DT v 0.17
## https://datatables.net/extensions/searchbuilder/examples/initialisation/columns.html
#
#    searchBuilder = (
#            columns = list(1,2,3)
#        )
#    searchCols = list(
#      NULL,
#      NULL,
#      NULL,
#      list(search = '["disability"]'),
#      NULL
#      ))
##
#  )

### ORIGINAL
#datatable(data,
#    options = list(),
#    rownames=FALSE,
##    filter = "top",
#    escape = FALSE,
#    )

## The download butons don't save the HTML...
#datatable(data,
#    rownames=FALSE,
##    filter = "top",
#    escape = FALSE,
#    extensions = 'Buttons',
#            options = list(dom = 'Blfrtip',
#                buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
#                lengthMenu = list(c(10,25,50,-1),
#                c(10,25,50,"All")))
#    )

```

Do you have a resource that you'd like to see added? Fill out our
<a href="https://forms.gle/VpkzjtbuAes3beAr7">suggestion form</a>.

## Disclaimer
This website offers resources and information, and is designed for educational
purposes only.
The T.H.R.I.V.E. website may contain links to external websites that are not
provided or maintained by or in any way affiliated with T.H.R.I.V.E.
Please note we don't guarantee the accuracy, relevance, timeliness, or
completeness of any information on these websites.
You should not rely on this information as a substitute for, nor does it
replace, professional medical advice, diagnosis or treatment.
